Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-01 paper/paper.tex
Update paper

\begin{abstract}
Litrepl is a text processor tool for recognizing and evaluating code sections in
Markdown or LaTeX documents. Litrepl is designed as middleware aimed at
separating text editors from the programming language interpreter management
logic, thus contributing to the diversity of both.
\end{abstract}

>>>>

\begin{abstract}

Litrepl is a simple and lightweight text processing tool designed to recognize
and evaluate code sections within Markdown or LaTeX documents. This
functionality is useful for both batch document section evaluation and
interactive coding within a text editor, provided a straightforward integration
is established.

\end{abstract}
